---
title: "Example Toggle"
format: html
engine: knitr
filters:
- toggle
---

# Overview

This document demonstrates how to use the `toggle` filter in Quarto. The filter allows you to control the visibility of code chunks based on a custom attribute.

## Usage

To use the `toggle` filter, you need to specify a custom attribute in your code chunk options. The attribute can be set to `true` or `false`, which will determine whether the code chunk is displayed or hidden in the output.

Let's look at an example of it in action:

```{r}
#| toggle: true
print("Hello, world!")
```

If the `toggle` attribute is set to `false` or is missing, the toggle option will not be available in the rendered document.

```{r}
#| toggle: false
print("Goodbye, world!")
```

```{r}
print("Missing, world!")
```

## Other special cases 

STDError Testing:

```{r}
#| toggle: true
warning("This is a warning message.")
```

Graph testing: 
```{r}
#| toggle: true
plot(1:10, 10:1)
```

Multi-line testing:

```{r}
#| toggle: true
print("This is a multi-line code chunk.")
print("It should be displayed when the toggle is set to true.")

plot(1:10, 10:1)
print("This is the final line.")
```