---
title: "Data Analysis Demo"
subtitle: "Document-wide toggle in action"
format:
  html:
    toc: true
extensions:
  toggle:
    output-toggle: true    # Enable toggle buttons for all cells
    global-toggle: true    # Allow toggling all outputs at once
filters:
  - toggle
---

This demo shows toggle enabled for every cell. Readers can hide outputs as
they work through the analysis, revealing results only when ready.

The floating button in the corner toggles everything at once.

## Configuration

```yaml
extensions:
  toggle:
    output-toggle: true
    global-toggle: true
```

## Loading the Data

We'll analyze the `mtcars` dataset: 32 cars from 1974 Motor Trend magazine.

```{r}
data(mtcars)
cat("Dataset dimensions:", nrow(mtcars), "rows,", ncol(mtcars), "columns\n")
```

```{r}
head(mtcars, 5)
```

## Exploratory Analysis

### Fuel Efficiency

Miles per gallon ranges from gas-guzzlers to relatively efficient:

```{r}
summary(mtcars$mpg)
```

```{r}
hist(mtcars$mpg,
     main = "Distribution of MPG",
     xlab = "Miles per Gallon",
     col = "steelblue",
     border = "white")
```

### Engine Size

Most cars have either 4, 6, or 8 cylinders:

```{r}
table(mtcars$cyl)
```

```{r}
barplot(table(mtcars$cyl),
        main = "Cars by Cylinder Count",
        xlab = "Cylinders",
        ylab = "Count",
        col = c("#4e79a7", "#f28e2b", "#e15759"))
```

## Relationships

### MPG vs Weight

Heavier cars use more fuel:

```{r}
cor(mtcars$mpg, mtcars$wt)
```

```{r}
plot(mtcars$wt, mtcars$mpg,
     main = "Weight vs MPG",
     xlab = "Weight (1000 lbs)",
     ylab = "Miles per Gallon",
     pch = 19,
     col = "steelblue")
abline(lm(mpg ~ wt, data = mtcars), col = "red", lwd = 2)
```

### MPG by Transmission

Manual transmissions tend to be more efficient:

```{r}
aggregate(mpg ~ am, data = mtcars, FUN = mean)
```

```{r}
boxplot(mpg ~ am, data = mtcars,
        names = c("Automatic", "Manual"),
        main = "MPG by Transmission Type",
        ylab = "Miles per Gallon",
        col = c("#f28e2b", "#4e79a7"))
```

## Summary

This demo showed toggle enabled document-wide with `output-toggle: true`.
Every code cell got a toggle button, letting readers hide outputs as they
work through the analysis.

The floating global button in the bottom-right corner toggles all outputs at
once—useful for quickly clearing the page or revealing everything.
