---
title: "Global Control"
subtitle: "One button for the whole page"
format:
  html:
    toc: true
extensions:
  toggle:
    output-toggle: true
    global-toggle: true
filters:
  - toggle
---

For long documents with many outputs, clicking each toggle individually gets
tedious. The global toggle button lets you hide or show everything at once.

Look in the bottom-right corner of your screen. You should see a floating
"Toggle All Outputs" button.

## Configuration

Add `global-toggle: true` to your settings:

```yaml
extensions:
  toggle:
    output-toggle: true
    global-toggle: true
```

::: {.callout-note appearance="simple"}
Global toggle is a document-level feature. There's no cell-level equivalent
since it wouldn't make sense for a single cell to control the whole page.
:::

## Try It

Click the floating button to hide all outputs. Click again to show them.

::: {.panel-tabset}

### Example

```{r}
print("Output 1")
```

```{r}
print("Output 2")
```

```{r}
print("Output 3")
```

```{r}
print("Output 4")
```

### Source

````md
```{{r}}
print("Output 1")
```

```{{r}}
print("Output 2")
```

```{{r}}
print("Output 3")
```

```{{r}}
print("Output 4")
```
````

:::

## Still Works with Individual Toggles

After using the global button, you can still click individual toggles to show
or hide specific outputs. The global button sets everything to the same state;
individual buttons fine-tune from there.

::: {.panel-tabset}

### Example

```{r}
#| output-hidden: true
print("I start hidden, but the global button affects me too.")
```

### Source

````md
```{{r}}
#| output-hidden: true
print("I start hidden, but the global button affects me too.")
```
````

:::

## Summary

Use `global-toggle: true` to add a floating button that hides or shows all
outputs at once. Individual toggles still work for fine-grained control.
Useful for presentations, code review, and navigating long documents.
