---
title: "Quick Start"
subtitle: "Your first toggle button"
format:
  html:
    toc: true
extensions:
  toggle:
    output-toggle: true
filters:
  - toggle
---

The toggle button appears when you hover over a code block. It sits in the
top-right corner, next to the copy button if you have one enabled.

```{=html}
<style>
.demo-toggle-btn {
  display: inline-flex;
  align-items: center;
  gap: 0.3em;
  padding: 0.25em 0.5em;
  border: 1px solid var(--quarto-border-color, #dee2e6);
  border-radius: 4px;
  background: var(--quarto-bg, #fff);
  cursor: pointer;
  font-size: 0.9em;
  vertical-align: middle;
  transition: background-color 0.15s;
}
.demo-toggle-btn:hover {
  background: var(--quarto-hover-bg, #f8f9fa);
}
</style>
```

Here's what it looks like (click to try):

```{=html}
<button class="demo-toggle-btn" onclick="const c = this.querySelector('.chevron'); c.textContent = c.textContent === '▼' ? '▶' : '▼'" title="Click to toggle"><span class="chevron">▼</span> Output</button>
<p></p>
```


- **▼** means output is visible (click to hide)
- **▶** means output is hidden (click to show)

## Try It

Hover over any code block on this page. You'll see the button fade in on the upper right side of the code cell.

::: {.panel-tabset}

### Example

```{r}
print("Hello! Hover over this code block.")
```

```{r}
x <- 1:5
cat("Sum:", sum(x), "\n")
cat("Mean:", mean(x), "\n")
```

### Source

````md
```{{r}}
print("Hello! Hover over this code block.")
```

```{{r}}
x <- 1:5
cat("Sum:", sum(x), "\n")
cat("Mean:", mean(x), "\n")
```
````

:::

## Enabling Toggle

You have two approaches: enable for specific cells, or enable document-wide.

### Per-Cell

::: {.panel-tabset}

#### Example

```{r}
#| toggle: true
summary(iris)
```

#### Source

````md
```{{r}}
#| toggle: true
summary(iris)
```
````

:::

### Document-Wide

Enable for all cells in your YAML header:

```yaml
extensions:
  toggle:
    output-toggle: true
```

This page uses document-wide configuration, so every code cell has a button.

## Disabling for Specific Cells

When toggle is enabled document-wide, you can turn it off for individual cells:

::: {.panel-tabset}

### Example

```{r}
#| toggle: false
print("This output is always visible. No button here.")
```

### Source

````md
```{{r}}
#| toggle: false
print("This output is always visible. No button here.")
```
````

:::

This is useful when you have results that should always be visible, like final
conclusions or key findings.

## Summary

Toggle buttons give readers control over output visibility. Enable them
document-wide with `output-toggle: true`, or per-cell with `#| toggle: true`.
Override either direction as needed.

**Next:** [Hide outputs by default](qtoggle-hidden-default.qmd),
[sync multiple outputs](qtoggle-sync-mode.qmd), or
[add a global button](qtoggle-global-toggle.qmd).
