---
title: "Nested Containers"
subtitle: "Toggle works inside tabsets, callouts, and more"
format:
  html:
    toc: true
extensions:
  toggle:
    output-toggle: true
filters:
  - toggle
---

Toggle buttons work regardless of where your code cells live. Tabsets,
callouts, columns, `<details>` elements: the extension finds your code and
attaches buttons correctly.

## Configuration

This page uses document-wide toggle:

```yaml
extensions:
  toggle:
    output-toggle: true
```

## Tabsets

::: {.panel-tabset group="tabset-demo"}

### Example

::: {.panel-tabset}

#### R

```{r}
cat("R code inside a tabset\n")
summary(1:10)
```

#### Python

```{python}
print("Python code inside a tabset")
import math
print(f"Pi = {math.pi:.6f}")
```

:::

### Source

````md
::: {.panel-tabset}

#### R

```{{r}}
cat("R code inside a tabset\n")
summary(1:10)
```

#### Python

```{{python}}
print("Python code inside a tabset")
import math
print(f"Pi = {math.pi:.6f}")
```

:::
````

:::

## Callouts

::: {.panel-tabset group="callout-demo"}

### Example

::: {.callout-note appearance="simple"}
## Code in a Note

```{r}
cat("This code lives inside a callout\n")
```
:::

::: {.callout-warning appearance="simple"}
## Warning with Code

```{python}
print("Toggle works in warnings too")
```
:::

::: {.callout-tip appearance="simple" collapse="true"}
## Collapsed Callout

Click the callout to expand, then toggle the output:

```{r}
cat("Hidden inside a collapsed callout\n")
```
:::

### Source

````md
::: {.callout-note appearance="simple"}
## Code in a Note

```{{r}}
cat("This code lives inside a callout\n")
```
:::

::: {.callout-warning appearance="simple"}
## Warning with Code

```{{python}}
print("Toggle works in warnings too")
```
:::

::: {.callout-tip appearance="simple" collapse="true"}
## Collapsed Callout

Click the callout to expand, then toggle the output:

```{{r}}
cat("Hidden inside a collapsed callout\n")
```
:::
````

:::

## Details Elements

::: {.panel-tabset group="details-demo"}

### Example

<details>
<summary>Click to expand</summary>

```{r}
cat("Code nested inside a <details> element\n")
```

</details>

<details open>
<summary>Already expanded</summary>

```{python}
print("This details element starts open")
```

</details>

### Source

````md
<details>
<summary>Click to expand</summary>

```{{r}}
cat("Code nested inside a <details> element\n")
```

</details>

<details open>
<summary>Already expanded</summary>

```{{python}}
print("This details element starts open")
```

</details>
````

:::

## Columns

::: {.panel-tabset group="columns-demo"}

### Example

::: {.columns}

::: {.column width="50%"}
**Left Column**

```{r}
cat("Left side\n")
```
:::

::: {.column width="50%"}
**Right Column**

```{python}
print("Right side")
```
:::

:::

### Source

````md
::: {.columns}

::: {.column width="50%"}
**Left Column**

```{{r}}
cat("Left side\n")
```
:::

::: {.column width="50%"}
**Right Column**

```{{python}}
print("Right side")
```
:::

:::
````

:::

## Nested Combinations

A tabset inside a callout inside a div:

::: {.panel-tabset group="nested-demo"}

### Example

::: {.border .p-3}

::: {.callout-note appearance="simple"}
## Deeply Nested

::: {.panel-tabset}

#### Tab A

```{r}
cat("Three levels deep\n")
```

#### Tab B

```{python}
print("Still works")
```

:::

:::

:::

### Source

````md
::: {.border .p-3}

::: {.callout-note appearance="simple"}
## Deeply Nested

::: {.panel-tabset}

#### Tab A

```{{r}}
cat("Three levels deep\n")
```

#### Tab B

```{{python}}
print("Still works")
```

:::

:::

:::
````

:::

## Summary

Toggle uses ID-based matching between code blocks and outputs. The DOM
structure doesn't matter. Nest your cells inside tabsets, callouts, columns,
or any combination. The extension finds them and attaches buttons correctly.
