---
title: "Custom Labels"
subtitle: "Name your buttons to match the content"
format:
  html:
    toc: true
extensions:
  toggle:
    output-toggle: true
    button-text: "Result"
filters:
  - toggle
---

"Output" is generic. When every button says the same thing, readers lose
context. Custom labels tell them what they'll find before they click.

This page uses "Result" as the default, but individual cells override it with
context-specific labels.

## Configuration

Set a document-wide default:

```yaml
extensions:
  toggle:
    output-toggle: true
    button-text: "Result"
```

Or label specific cells with `#| button-text: "Plot"`.

```{{r}}
#| button-text: "Plot"
plot(1:10, main = "Sample Data", pch = 19, col = "steelblue")
```

## Examples

### Default Label

These cells inherit "Result" from the document settings:

::: {.panel-tabset}

#### Example

```{r}
2 + 2
```

```{r}
print("Standard label from document config")
```

#### Source

````md
```{{r}}
2 + 2
```

```{{r}}
print("Standard label from document config")
```
````

:::

### Context-Specific Labels

Override per-cell when the content calls for it:

::: {.panel-tabset}

#### Example

```{r}
#| button-text: "Solution"
factorial(5)
```

```{r}
#| button-text: "Plot"
plot(1:10, main = "Sample Data", pch = 19, col = "steelblue")
```

#### Source

````md
```{{r}}
#| button-text: "Solution"
factorial(5)
```

```{{r}}
#| button-text: "Plot"
plot(1:10, main = "Sample Data", pch = 19, col = "steelblue")
```
````

:::

## Summary

Use `button-text` to replace the generic "Output" label with something
meaningful. Set a document default, then override per-cell as needed. Good
labels ("Solution", "Plot", "Debug") tell readers what to expect before they
click.
