---
title: "Hide by Default"
subtitle: "Start collapsed, reveal on demand"
format:
  html:
    toc: true
extensions:
  toggle:
    output-toggle: true
    output-hidden: true
filters:
  - toggle
---

Sometimes you want outputs hidden until readers actively choose to see them.
This keeps pages clean while making details available on demand.

Every output on this page starts hidden. Click the toggle buttons to reveal
them.

## Configuration

Add `output-hidden: true` to your settings:

```yaml
extensions:
  toggle:
    output-toggle: true
    output-hidden: true
```

Or set it on individual cells with `#| output-hidden: true`.

## Examples

These outputs are hidden until you click:

::: {.panel-tabset}

### Example

```{r}
print("You found me!")
```

```{r}
for (i in 1:3) {
  cat("Line", i, "\n")
}
```

### Source

````md
```{{r}}
print("You found me!")
```

```{{r}}
for (i in 1:3) {
  cat("Line", i, "\n")
}
```
````

:::

## Showing Specific Cells

Even when the document default is hidden, you can force specific outputs to
show:

::: {.panel-tabset}

### Example

```{r}
#| output-hidden: false
print("I'm visible by default, despite the document setting.")
```

### Source

````md
```{{r}}
#| output-hidden: false
print("I'm visible by default, despite the document setting.")
```
````

:::

## Summary

Use `output-hidden: true` to start outputs collapsed. Readers click to reveal.
Override with `output-hidden: false` on cells that should always show.

Works well for problem sets (hide solutions), reports (hide supporting
details), and tutorials (reveal answers progressively).
