---
title: "Sync Multiple Outputs"
subtitle: "Toggle related outputs together"
format:
  html:
    toc: true
extensions:
  toggle:
    output-toggle: true
filters:
  - toggle
---

When a single code cell produces multiple outputs (a printed summary, a plot,
a table), you might want them to toggle together rather than separately. Sync
mode does exactly that.

Synced toggle buttons have a **blue left border** so you can tell they're
linked.

## Configuration

Enable sync mode in your settings:

```yaml
extensions:
  toggle:
    output-toggle: true
    output-sync: true
```

Or per-cell with `#| output-sync: true`.

## Individual Mode (Default)

Without sync, each output gets its own independent button. Click one and only
that output hides.

::: {.panel-tabset}

### Example

```{r}
print("First output - has its own toggle")
```

```{r}
print("Second output - toggles independently")
```

### Source

````md
```{{r}}
print("First output - has its own toggle")
```

```{{r}}
print("Second output - toggles independently")
```
````

:::

## Synced Mode

With sync enabled, all outputs from the cell toggle together. Notice the blue
border on the buttons. Click any of them and all outputs respond.

::: {.panel-tabset}

### Example

```{r}
#| output-sync: true
cat("Part 1: Summary\n")
cat("Mean:", mean(1:10), "\n")
cat("SD:", sd(1:10), "\n\n")
cat("Part 2: Visual\n")
barplot(1:5, names.arg = LETTERS[1:5], col = "steelblue")
cat("\nPart 3: Complete\n")
```

### Source

````md
```{{r}}
#| output-sync: true
cat("Part 1: Summary\n")
cat("Mean:", mean(1:10), "\n")
cat("SD:", sd(1:10), "\n\n")
cat("Part 2: Visual\n")
barplot(1:5, names.arg = LETTERS[1:5], col = "steelblue")
cat("\nPart 3: Complete\n")
```
````

:::

## Mixing Modes

You can use document-wide sync for most cells and override specific ones:

::: {.panel-tabset}

### Example

```{r}
#| output-sync: false
cat("This cell uses individual mode\n")
cat("Each line toggles separately\n")
```

### Source

````md
```{{r}}
#| output-sync: false
cat("This cell uses individual mode\n")
cat("Each line toggles separately\n")
```
````

:::

## Summary

Use `output-sync: true` when multiple outputs from the same cell belong
together conceptually. Synced buttons show a blue border and toggle as a
group. Use individual mode when readers should control each output separately.
