---
title: "Toggle for All Cells"
format: 
  html:
    toc: true
toggle:
    output-toggle: true    # Enable toggle buttons for all cells
    output-hidden: false   # Show outputs initially (default)
filters:
  - toggle
---

This page demonstrates how to globally enable toggle functionality
for all code cells, rather than enabling it on a per cell configuration.
This approach allows you to skip individual cell configurations unless
you want to override the global behavior.

## Setup

To enable toggle for all cells, add this to your document's YAML header:

```yaml
---
title: "Your Document Title"
format: html
toggle:
  output-toggle: true    # Automatically add toggle to all cells
  output-hidden: false   # Show outputs by default
filters: [toggle]
---
```

With this set, every code cell that produces an output gets a toggle button 
automatically and outputs are visible by default. Readers can hide them if 
they choose.

This means: 

- No need to add `toggle: true` to individual cells as it will apply to all.
- Outputs are visible by default (readers can hide them)
- Consistent experience across your entire document

Hover over code blocks to see toggle buttons. `"⌄"` = visible, `"›"` = hidden.

## Python Examples

### Output

```{python}
print("Hello, world!")
print("This has a toggle button.")
```

### Math Operations

```{python}
numbers = [1, 2, 3, 4, 5]
print(f"Sum: {sum(numbers)}")
print(f"Average: {sum(numbers)/len(numbers)}")
```

### Plotting with Matplotlib

```{python}
import matplotlib.pyplot as plt
plt.plot([1, 2, 3], [1, 4, 9], 'o-')
plt.title("Simple Plot")
plt.show()
```

## R Examples

### Statistics Calculations

```{r}
data <- c(10, 20, 30, 40, 50)   
cat("Mean:", mean(data), "\n")
cat("Max:", max(data), "\n")
```

### Graphing with Base R

```{r}
barplot(c(23, 45, 32), names.arg = c("A", "B", "C"))
```

## Override Options

### Always Show

No toggle button will be added, output is always visible.

```{python}
#| toggle: false
print("Always visible - no toggle button")
```

### Hidden by Default

Starts hidden - click toggle to show

```{python}
#| output-hidden: true
print("You've clicked the toggle button to show me!")
```

## Other Languages

### Bash

```{bash}
echo "Current date:"
date
```
